%use mybib.bib for bibliography. bibtex is used for bibliography
\documentclass[journal]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
%\usepackage[section]{placeins}
%\usepackage{subcaption}
\usepackage{array}
\usepackage[export]{adjustbox}
\usepackage{tabu}
\usepackage{tabularx}
\usepackage{listings}
\usepackage{siunitx}
\usepackage{siunitx}
\usepackage{ wasysym }
\usepackage[usenames, dvipsnames]{color}
\usepackage{diagbox}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\ifCLASSINFOpdf

\else

\fi


\hyphenation{op-tical net-works semi-conduc-tor}


\begin{document}

\title{A Graph Search Based Energy Management Strategy for Grid-Connected Distributed Energy Resources Considering Present and Future System Status}

\author{\IEEEauthorblockN{Alvi Newaz\IEEEauthorrefmark{1}, Md. Omar Faruque\IEEEauthorrefmark{0}}
\IEEEauthorblockA{\\The Department of Electrical and Computer Engineering at the FAMU-FSU College of Engineering \\ Center for Advanced Power Systems, Florida State University \\
2000 Levy Avenue, Tallahassee, FL., USA.
%Wherever\\
Email: an15m@my.fsu.edu\IEEEauthorrefmark{1}}}


\maketitle
\IEEEpeerreviewmaketitle

\begin{abstract}
This paper presents a real-time  energy management system (EMS) for distribution systems or microgrids containing distributed energy resources (DERs). The EMS aims to optimize the use of dispatchable grid-connected DERs to achieve the minimum cost of operation while taking into consideration line constraints and present and future status of the grid. To achieve this the ESM algorithm generates a graph based on the present and forecasted data and uses the A* search algorithm to find the minimum cost. The algorithm is validated using off-line phasor simulation using pricing schemes from New York Independent System Operator (NYISO) and Pacific Gas and Electric (PG\&E) and system data from the sunshine state solar grid initiative (SUNGRIN) report. The real-time controller hardware in the loop (CHIL) validation of the algorithm is performed by simulating a full electromagnetic transient model of the system in a digital real-time simulator. The results are comparable to the offline simulation and show significant cost savings due to considering future status of the grid compared to optimizing based on only the current system status.

\end{abstract}

\input{01_intro}

\input{02_problem_formulation}

\input{03_energy_management_solution}

\input{04_test_system}

\input{05_offline_sim}

\input{06_real_time}

\input{07_conclusion}

\bibliographystyle{IEEEtran}
\bibliography{mybib.bib}

% \ifCLASSOPTIONcaptionsoff
%   \newpage
% \fi

\end{document}
